### 2013-12-17 proposal/background.tex
Moving stuff because I'm going insane with everything in one big directory.

Much work has been completed on information-flow languages.  Projects like FlowCaml\cite{simonet2003flow}, JIF\cite{myers2000protecting}, Fabric\cite{liu2009fabric}, and more offer complete production languages with strong information-flow security guarantees.  These languages are aimed for deployment in industry, where their security properties are relied upon for the integrity and confidentiality of sensitive information.  Like all software systems, the compilers for these languages are not free of bugs; these bugs can compromise the very security policies that the languages seek to enforce.  Other languages have addressed this problem by building verified compilers\cite{leroy2012compcert,okuma2003executing,chlipala2010verified,berghofer2004extracting,strecker2002formal,necula1998design,necula2002proof}.  Verified compilers are free of implementation-level bugs; they guarantee that the semantics of the source program are identical to the semantics of the destination language\cite{necula1998design}.  As of yet, no verified compiler exists for an information-flow language, leaving users to choose between a provably correct compiler for an insecure language and a potentially-buggy compiler for a secure language.

>>>>

Much work has been completed on information-flow languages.  Projects
like FlowCaml\cite{simonet2003flow}, JIF\cite{myers2000protecting},
Fabric\cite{liu2009fabric}, and more offer complete production languages
with strong information-flow security guarantees.  These languages are
aimed for deployment in industry, where their security properties are
relied upon for the integrity and confidentiality of sensitive
information.  Like all software systems, the compilers for these
languages are not free of bugs; these bugs can compromise the very
security policies that the languages seek to enforce.  Other languages
have addressed this problem by building verified
compilers\cite{leroy2012compcert,okuma2003executing,chlipala2010verified,berghofer2004extracting,strecker2002formal,necula1998design,necula2002proof}.
Verified compilers are free of implementation-level bugs; they guarantee
that the semantics of the source program are identical to the semantics
of the destination language\cite{necula1998design}.  As far as we know,
no verified compiler exists for an information-flow language, leaving
users to choose between a provably correct compiler for an insecure
language and a potentially-buggy compiler for a secure language.
